Lawvere-Tierney Sheafification in Homotopy Type Theory

### 2016-04-07 paper/paper_lipics.tex
finish

\subsection{Overview of the Result}

@@

The development uses the new universe polymorphism feature of
Coq~\cite{sozeau2014universe}. However, it still lacks some features, and
in the formalization, we had to use the \texttt{type-in-type} option, to handle
the universe issues we faced.

\nt{explain why it is acceptable}

@@

\newpage
\appendix
\section{Proofs}

@@

In this section, we present how to use the sheafification modality to
define a transformation of Martin-Löf type theory into
itself\footnote{We define the translation on Martin-Löf type theory,
  but it could also be done for CIC as well.} as it has been done for
forcing~\cite{jaber2012extending}.

>>>>

\subsection{Overview of the Result}
\label{ssec:overview}

@@

The development uses the new universe polymorphism feature of
Coq~\cite{sozeau2014universe}. However, it still lacks some features, and
in the formalization, we had to use the \texttt{type-in-type} option, to handle
the universe issues we faced. If not totally satisfactory, this option
is a convenient way to write the Coq code, the following
universes issues being checked on paper, like in the library
Unimath\footnote{\url{https://github.com/UniMath}, {Vladimir
    Voevodsky, Benedikt Ahrens, Daniel Grayson and others}}.

@@

\newpage
\appendix
\section{Proofs}
As said in section~\ref{sec:sheafification}, some proofs were ommited
in the paper, due to space reason. The reader can find the key points
here, and see the complete proofs in the Coq formalization, at
\url{https://github.com/KevinQuirin/sheafification}.

@@

In section~\ref{ssec:overview}, we announce that sheafification can be
seen a translation of type theories\footnote{We define the translation on Martin-Löf type theory,
  but it could also be done for CIC as well.}, as it has been done for
forcing~\cite{jaber2012extending}. Actually, this is not a specific
property of sheafification, but something shared by all modalities. We
hence don't explicit it in the paper, but we do in this appendix.
